---
title: "Case study data"
author:
- name: Xiaotao Shen (https://www.shenxt.info/)
date: "Created on 2022-03-07 and updated on `r Sys.Date()`"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: yes
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{case_study_data}
  %\VignettePackage{tidymass}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
```

# **MS1 Raw data**

The raw data of the case study (MS1, mzML format) is accessible on `MetaboLights` with [MTBLS1122 (HILIC positive)](https://www.ebi.ac.uk/metabolights/MTBLS1122), [MTBLS1124 (HILIC negative)](https://www.ebi.ac.uk/metabolights/MTBLS1124/descriptors), [MTBLS1122 (RPLC positive)](https://www.ebi.ac.uk/metabolights/MTBLS1129/descriptors) and [MTBLS1130 (RPLC negative)](https://www.ebi.ac.uk/metabolights/MTBLS1130/descriptors).

# **MS2 raw data**

The raw data of the case study (MS2, mgf format) is accessible [here](https://drive.google.com/file/d/1fR75tWp9jqp8vuWq85GvDGJ864Pb6AH2/view?usp=sharing).

# **Processed data**

The processed data (“mass_dataset” class) from the `massProcesser` package are [available here](https://drive.google.com/file/d/1BxILAJYAHBiIKLKaAcsTY-tgMCWV2YcO/view?usp=sharing).

# **Other data**

You can also download all the other dataset which are necessary for reproducible analysis for case_study.

1. [data_cleaning](https://drive.google.com/file/d/1Rg5wzSrIQm5i4Eb6TyK5MrOs342UbOPK/view?usp=sharing)

2. [metabolite_annotation](https://drive.google.com/file/d/1lht4LAG8VKGHqRceslPUc-dZVm72o7eD/view?usp=sharing)

3. [pathway_enrichment](https://drive.google.com/file/d/1ysz9opVjiCVNpLC0R75O2SD56h_2EyPg/view?usp=sharing)

4. [sample_info](https://drive.google.com/file/d/1v47gH9jvcARIuG8DUwSY7RgC58msjNo2/view?usp=sharing)

5. [Statistical_analysis](https://drive.google.com/file/d/1V7U7R12Qpsh3QR3c82F9dGq9x4QxRcpj/view?usp=sharing)

# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```