---
title: "Create mass_dataset class from other tools"
author:
- name: Xiaotao Shen (https://www.shenxt.info/)
date: "Created on 2022-02-25 and updated on `r Sys.Date()`"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: yes
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{create_mass_dataset}
  %\VignettePackage{tidymass}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
```

If you don't want to use the `massprocesser` for raw data processing, you can absolutely use other tools (mzMine or MS-DIAL). Then you can just use the functions from `massdataset` convert results from them to `mass_dataset` class.

# **mzMine feature table to `mass_dataset` class**


We can also directory convert feature table from [mzMine](http://mzmine.github.io/) to `mass_dataset` class.

An example feature table from mzMine.

```{r,eval=TRUE, echo=FALSE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
library(massdataset)
data("mzmine_table")
library(kableExtra)
library(magrittr)
kbl(mzmine_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "600px")
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data("mzmine_table")
object =
   convet_mzmine2mass_dataset(x = mzmine_table)
object
```

# **MS-DIAL feature table to `mass_dataset` class**

We can also directory convert feature table from [MS-DIAL](http://prime.psc.riken.jp/compms/msdial/main.html) to `mass_dataset` class.

An example feature table from MS-DIAL.

```{r,eval=TRUE, echo=FALSE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
library(massdataset)
data("msdial_table")
library(kableExtra)
library(magrittr)
kbl(msdial_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "600px")
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data("msdial_table")
object =
   convert_msdial2mass_dataset(x = msdial_table)
object
```

# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```